The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-08-03 paper/mnras/paper.tex
Fix

More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
described above.   These calculations show just how dramatically {\em different} the compact binary populations of galaxies
with different present-day {\em masses} %but different star formation histories 
could be.   The dwarf galaxies have an
exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13} relative to the more massive galaxies.  The precise details of their chemical
evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
the conservative choices described above for the dependence of rate on metallicity.  The progenitors and electromagnetic counterparts of future gravitational wave events are overall much more likely to be located in nearby dwarf galaxies with a large population of low metallicity stars.

>>>>

More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
described above.   These calculations show just how dramatically {\em different} the compact binary populations of galaxies
with different present-day {\em masses} %but different star formation histories 
could be.   The dwarf galaxies have an
exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13} relative to the more massive galaxies.  The precise details of their chemical
evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
the conservative choices described above for the dependence of rate on metallicity.  The progenitors (and, if present,
electromagnetic counterparts) of future binary black hole gravitational wave events are overall much more likely to be located in nearby dwarf galaxies with a large population of low metallicity stars.
